Figure for Weather Comparison

### 2025-09-02 Weather_com_figure_ABP.Rmd

# # Rename the variable to fit in the labels
# hum_names <- as_labeller(
#      c(`Rain_Total_sum_cm` = "Daily Rain Toal cm", `AirTemp_C_Average` = "Daily Average Air Temp C",`WindSpeed_Average_m_s` = "Daily Averge Wind Speed m/s"))
# 
# # Make the plot here
# ggplot(met_all_long, aes(x = ddate, y = obs, color = as.factor(Year)))+
#   geom_point()+ # point or line?
#   facet_grid(vars(variable), scales = "free", labeller = hum_names)+
#   labs(color='Year') + 
#   ylab("")+
#   xlab("Date")+
#   scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",
#              date_labels = "%B")+
#   theme_bw(base_size = 15) #size of all the text in the figure. 
# 
# 
#  # can change dimensions as you see fit 
# ggsave("figures/Met_com_2018_2023.png", width = 10, height = 8, dpi = 300, units = "in", device='png')
```
```{r Function to Make Plots}

@@

a <- met_all_long%>%
  filter(variable == VAR)%>%
ggplot(., aes(x = ddate, y = obs, color = as.factor(Year)))+
  geom_point()+ 
  labs(color='Year') +
  ylab(y_lab)+
  xlab("Date")+
  scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",
             date_labels = "%B")+
  theme_bw(base_size = 18) #size of all the text in the figure.

>>>>

# # Rename the variable to fit in the labels
# hum_names <- as_labeller(
#      c(`Rain_Total_sum_cm` = "Daily Rain Toal cm", `AirTemp_C_Average` = "Daily Average Air Temp C",`WindSpeed_Average_m_s` = "Daily Averge Wind Speed m/s"))
# 
# # Make the plot here
# ggplot(met_all_long, aes(x = ddate, y = obs, color = as.factor(Year)))+
#   geom_point()+ # point or line?
#   facet_grid(vars(variable), scales = "free", labeller = hum_names)+
#   labs(color='Year') + 
#   ylab("")+
#   xlab("Date")+
#   scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",
#              date_labels = "%B")+
#   theme_bw(base_size = 15) #size of all the text in the figure. 
# 
# 
#  # can change dimensions as you see fit 
# ggsave("figures/Met_com_2018_2023.png", width = 10, height = 8, dpi = 300, units = "in", device='png')
```

```{r Function to Make Plots}

@@

a <- met_all_long%>%
  filter(variable == VAR)%>%
ggplot(., aes(x = ddate, y = obs, color = as.factor(Year)))+
  geom_line()+ 
  labs(color='Year') +
  ylab(y_lab)+
  xlab("")+
  scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",
             date_labels = "%B")+
  theme_bw(base_size = 18) #size of all the text in the figure.
